Modi normali di oscillazione del Sole (Presentazione)

### 2017-06-16 MSS.tex
mf

Sezione d'urto collisionale di Rutherford:
\begin{align*}
&d\sigma=\frac{4\pi(Z_iZ_j)^2}{\mu^2(\vec{v}-\vec{v}')^4}\frac{d\chi}{\chi^3}\\
&\lambda=\max{(r_D,a_0)}$: $L=\int\frac{d\chi}{\chi}=\log{(\frac{1}{\chi_{min}})}\\
&\sigma_{ij}\propto \frac{e^4Z_i^2Z_j^2}{(KT)^2}\ln{\Lambda_{st}}\Label{eq:sruther}\ln{\Lambda_{ij}}\propto\ln{[1+0.18769(\frac{4KT\lambda}{Z_iZ_je^2})]}\Label{eq:clog}
\end{align*}

>>>>

Sezione d'urto collisionale di Rutherford:
\begin{align*}
d\sigma=\frac{4\pi(Z_iZ_j)^2}{\mu^2(\vec{v}-\vec{v}')^4}\frac{d\chi}{\chi^3}\Label{eq:dsruther}L=\int\frac{d\chi}{\chi}=\log{(\frac{1}{\chi_{min}})}\Label{eq:cL}\lambda=\max{(r_D,a_0)}:\Label{eq:maxb}
\end{align*}

\begin{align*}
\sigma_{ij}\propto \frac{e^4Z_i^2Z_j^2}{(KT)^2}\ln{\Lambda_{st}}\Label{eq:sruther}\ln{\Lambda_{ij}}\propto\ln{[1+0.18769(\frac{4KT\lambda}{Z_iZ_je^2})]}\Label{eq:clog}
\end{align*}
